Boundary Labeling for annotated documents

### 2018-01-20 LaTeX/Paper.tex
Paper: Re-wrote Section 2.1, changed Fig. 2.1. Program: No changes.

\documentclass[11pt,a4paper]{vutinfth}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{caption}
\usepackage{mathtools}
\usepackage{amssymb}
\usepackage[boxed,linesnumbered]{algorithm2e}
\usepackage{color}
%\usepackage[]{luatodonotes}
%\usepackage{wrapfig}

@@

\emph{Polylines} are a connected series of \emph{line segments}. Line segments are straight lines that contain each point between their starting and end point. 
\emph{Labels} hold additional information and are represented as boxes containing this information. They are usually placed in the \emph{label area} which is a rectangular area designated to hold labels. It is located next to of the bigger, rectangular \emph{text area}, which contains the document's text and all \emph{sites}, the points or objects that a label's information refers to. \change{If multiple label areas exist on different sides of the text area, we speak of \emph{multi-sided labeling}, otherwise we speak of \emph{one-sided labeling}. We will be using one-sided labeling in our implementation. Some space was left in between the text and label area, to make connecting sites to their labels easier, which we will call the \emph{routing area}.} The site and the label are connected via a \emph{leader}, a polyline that can be further classified by looking at the orientation of its segments: \emph{O-Segments} run orthogonally to the border of the label area. \emph{P-Segments} run parallel to the border of the label area, and as such must be combined with other segments for the leader to reach its destination. \emph{S-Segments} are not required to have any particular orientation, and simply connect their start and ending points in a straight line.
The leader's name is created by combining the name of the segments - for example, the blue leader from Fig~\ref{fig:term} would be classified as an OPOPO-Leader.
The location where a leader connects to the label is called the \emph{port}. It can be restricted to pre-defined positions. %TODO: Re-insert monotonicity

@@

%Beispiele von suboptimalen Lösungen einfügen? (Bilder)
Boundary labeling in text documents however, is rarely discussed, and only few papers exist about this topic. The programs that employ this style of annotation often also use rather simple algorithms, to mediocre results or make extensive use of the interactivity of a digital medium, showing annotations only on demand. However, the few papers that approach this topic add interesting information to the discussion. %Rewrite Sentence, I don't like it!

@@

\chapter{The Algorithm}

In our algorithm, the focus was put on keeping the text as readable as possible. This means that leaders aren't allowed to pass through words, which was implemented by enclosing each word in a bounding rectangle that leaders aren't allowed to pass through.
The leaders should also be kept as short as possible, so we restricted them to always be moving toward the label, even if the direct route is unavailable.%Wie drücke ich das als Formel aus?
We also wanted to use the space available in the labeling area as efficiently as possible, so labels are placed as far up as possible in order to maximize the space available to future labels at the cost of increased leader length.

>>>>

\documentclass[11pt,a4paper]{vutinfth}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{caption}
\usepackage{mathtools}
\usepackage{amssymb}
\usepackage[boxed,linesnumbered]{algorithm2e}
\usepackage{color}
\usepackage{subcaption}
%\usepackage[]{luatodonotes}
%\usepackage{wrapfig}

@@

\emph{Polylines} are a connected series of \emph{line segments}. Line segments are straight lines that contain each point between their starting and end point. 
\emph{Labels} hold additional information and are represented as boxes containing this information. They are usually placed in the \emph{label area} which is a rectangular area designated to hold labels. It is located next to of the bigger, rectangular \emph{text area}, which contains the document's text and all \emph{sites}, the points or objects that a label's information refers to. If multiple label areas exist on different sides of the text area, we speak of \emph{multi-sided labeling}, otherwise we speak of \emph{one-sided labeling}. We will be using one-sided labeling in our implementation. Some space was left in between the text and label area, to make connecting sites to their labels easier, which we will call the \emph{routing area}. The site and the label are connected via a \emph{leader}, a polyline that can be further classified by looking at the orientation of its segments: \emph{O-Segments} run orthogonally to the border of the label area. \emph{P-Segments} run parallel to the border of the label area, and as such must be combined with other segments for the leader to reach its destination. \emph{S-Segments} are not required to have any particular orientation, and simply connect their start and ending points in a straight line.
The leader's name is created by combining the name of the segments - for example, the blue leader from Fig~\ref{fig:term} would be classified as an OPOPO-Leader.
The location where a leader connects to the label is called the \emph{port}. It can be restricted to pre-defined positions. %TODO: Re-insert monotonicity

@@

%Beispiele von suboptimalen Lösungen einfügen? (Bilder)
Boundary labeling in text documents however, is rarely discussed, and only few papers exist about this topic. The programs that employ this style of annotation often also use rather simple algorithms, to mediocre results or make extensive use of the interactivity of a digital medium, showing annotations only on demand. However, the few papers that approach this topic add interesting information to the discussion.

@@

\chapter{The Algorithm}
%1 Zeile Einleitung hier einfügen - zb: Kapitelübersicht
\section{Problem Specification}
We limited the leaders to use exclusively O- and P-Segments, and banned them from passing through words. We also place labels as far up as possible to maximize the space remaining for  remaining placements. Additionally, a leader isn't allowed to be any longer as is necessary to connect a given Site with its label's port.

These restrictions are implemented as follows: We divided the text $T$ into separate lines $L=\{W,H\}$ which are in turn made up of words $W$ and whitespace $H$. Each word $w \in W$ is surrounded by a bounding rectangle $r$, %Definition schreiben?
which marks the space leaders aren't allowed to cross. For a graphical representation see Fig.~\ref{fig:wbound}.

\begin{figure}
 \centering
 \begin{subfigure}[b]{\textwidth}
 \centering
  \includegraphics[]{WordBoundaries.png}
  \caption{\label{fig:wbound}}
 \end{subfigure}
 \\
 ~\\%There's probably a better way for this...
 \begin{subfigure}[b]{\textwidth}
 \centering
  \includegraphics[]{RoutingGraph_edited.png}
  \caption{\label{fig:rgraph}}
 \end{subfigure}
 \caption{Visualization of the space reserved for the text, and the resulting graph.}
\end{figure}

Since we only allowed the Usage of O- and P-Segments in leaders, the only way for a leader to cross through a line of text is with a P-Segment through whitespace, whereas O-Segments are only usable between lines. Therefore, we can create a routing graph $G=\langle V,E\rangle$ whose Edges $E$ reflect the legal paths a leader can take within $T$.
For each whitespace character $w \in W$, one vertex is placed above and below, so that it has the maximum distance from both of its adjacent lines. The start and end of each line also recieve a pair of vertices each. Sites will be represented by the insertion of additional vertices at appropriate places. The edges between the vertices are all perfectly horizontal or vertical, and do neither intersect with any bounding rectangle, nor any vertices other than their starting and ending vertex.The resulting graph looks similar to Fig.~\ref{fig:rgraph}.

Each edge has a capacity of 1, meaning that no more than one leader is allowed to pass through it. Leaders also aren't allowed to cross one another, as it is hard to discern between intersections and two leaders curving away from each other. This is realized by forcing leaders to incorporate as many P-Segments as early as possible while still following all previous restrictions, and forbidding leaders from entering the space to the top left of already successfully routed leader's sites.
%In our algorithm, the focus was put on keeping the text as readable as possible. This means that leaders aren't allowed to pass through words - they can only use the space between words and in between lines.
%Additionally, we wanted to maximize the usage of the label area's space, even if we have to move labels further from their sites than needed. 
%Finally, we wanted to keep the leader's length low for any given combination of labels and site placements, so every segment of a leader has to decrease the remaining distance between the site and its label's port.

%\begin{figure}
% \captionsetup{justification=centering, margin=0.75cm}
% \centering
%  \makebox[\textwidth][c]{\includegraphics[scale=0.9]{FromTextToGraph.png}}
%  \caption{Visualization of the space reserved for the text, and the resulting graph.}
% \label{fig:ttg}
%\end{figure}

%These properties were modelled by creating a rectangle around each word that no leaders may pass through. If this is done for all words in a paragraph, the remaining available space for routing resembles a grid, like in Fig.\ref{fig:ttg}a.

%Since the layout encourages the usage of P- and O-segments, we decided to represent the possible routes by creating a graph which has its vertices located whenever multiple directions are available - in between lines, above or below whitespace characters. The graph's edges represent the different possible segments of a leader and connect each vertex with the closest vertices directly above, below or to the sides, given that no text is blocking the connection. The resulting graph looks similar to the one in Fig.~\ref{fig:ttg}b.

%For ease of visualisation, we limited the number of leaders per edge to one, and forbid the leaders to cross one another, as this could be mistaken for two leaders touching each other at the corners. We also decided to place the annotations in the order in which they appear in the text, and always place their port above the leader's source, which means that crossings are inevitable if a leader is located above and to the left of an earlier leader. To ensure this never happens, leaders aren't allowed to enter the top left quadrant of a source vertex, unless no routing could be found for that vertex, which means there won't be any leaders to collide with. Additionally, to keep the leader's length minimal, each leader is only allowed to move towards the source, which places a hard limit on how far up a leader is allowed to go, and restricts the possible choices at each node to edges that allow the leader to move in that direction.
%To maximize the space available to subsequent annotations, each label is placed as far up as possible. This also means that if there's no placement available that is above its leader's source, the annotation cannot be placed, as we previously restricted the leader's movement.

%This was implemented by enclosing each word in a bounding rectangle that leaders aren't allowed to pass through.
%The leaders should also be kept as short as possible, so we restricted them to always be moving toward the label, even if the direct route is unavailable.%Wie drücke ich das als Formel aus?
%We also wanted to use the space available in the labeling area as efficiently as possible, so labels are placed as far up as possible in order to maximize the space available to future labels at the cost of increased leader length.

\section{Description}
